---
title: "Pre-Processed Data"
author:
- Lourdes Sofía Elizondo Guajardo
- Daniela Diaz Delgado
- Bernardo Ortega Chávez
- Gabriel González Bataller
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
subtitle:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("gmodels")
library("ggplot2")
library("pROC")
library("rpart")
library("rattle")
library("rpart.plot")
library("tinytex")
library("kableExtra")
library("ROSE")
library("tibble")
library("bitops")
library("tidyquant")
library("knitr")
library("plotly")
library("Sim.DiffProc")
library("readxl")
```

# Population data: Infonavit's portfolio today

## Data Analysis

N: Número de Créditos Formalizados
I: Importe de Cheque
M: Monto de Crédito Infonavit

```{r}
NTotal<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 1)
NTipoDeProducto<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 2)
NLinea<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 3)
NClasifDeVivienda<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 4)
NIngreso<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 5)
NEdad<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 6)
NEstado<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/NumeroDeCreditosFormalizados.xlsx", sheet = 7)

ITotal<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 1)
ITipoDeProducto<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 2)
ILinea<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 3)
IClasifDeVivienda<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 4)
IIngreso<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 5)
IEdad<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 6)
IEstado<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/ImporteDeCheque.xlsx", sheet = 7)

MTotal<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 1)
MTipoDeProducto<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 2)
MLinea<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 3)
MClasifDeVivienda<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 4)
MIngreso<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 5)
MEdad<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 6)
MEstado<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/MontoDeCreditoInfonavit.xlsx", sheet = 7)
```

## Past Due Portfolio Analysis
```{r}
```

# Sample data: mortgage loans 2013-2020

## Data
```{r}
y2013<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 2)
y2014<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 3)
y2015<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 4)
y2016<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 5)
y2017<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 6)
y2018<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 7)
y2019<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 8)
y2020<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 9)
y2021<-read_excel("/Users/lulyelizondo/Desktop/DATATESIS/DATOSMUESTRA.xlsx", sheet = 10)

data1<-rbind(y2013,y2014,y2015,y2016,y2017,y2018,y2019,y2020,y2021)
nrow(data1)
```

```{r}
data2<-subset(data1, select = -c(ENTIDAD,CLAVE_MUNICIPIO,MUNICIPIO,ORGANISMO,ACCIONES))

data2$AÑO<-factor(data2$AÑO)
data2$MES_ACUMULADO<-factor(data2$MES_ACUMULADO)
data2$CLAVE_ENTIDAD<-factor(data2$CLAVE_ENTIDAD)
data2$MODALIDAD<-factor(data2$MODALIDAD)
data2$DESTINO<-factor(data2$DESTINO)
data2$TIPO<-factor(data2$TIPO)
data2$GENERO<-factor(data2$GENERO)
data2$EDAD<-factor(data2$EDAD)
data2$INGRESO<-factor(data2$INGRESO)
data2$VALOR_VIVIENDA<-factor(data2$VALOR_VIVIENDA)
data2$MONTO<-as.numeric(data2$MONTO)
data2$CLAVE<-factor(data2$CLAVE)

summary(data2)
str(data2)
head(data2)
tail(data2)
```

## Sample Data Analysis
```{r}
```

## Adjust Sample to Match Population's Characteristics 
```{r}
```

## Asign Variable Status
```{r}
```

# Credit Risk Model

## Logistic Regression
```{r}
```

## Evaluation
```{r}
```

## Regional Analysis
```{r}
```

# Building a Cross-Subsidy Scheme

## Asigning an Interest Rate
```{r}
```

# Comparative Statics & Tests
```{r}
```