---
title: "Datos"
author:
- Lourdes Sofía Elizondo Guajardo
- Daniela Diaz Delgado
- Bernardo Ortega Chávez
- Gabriel González Bataller
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
subtitle: "Test"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("gmodels")
library("ggplot2")
library("pROC")
library("rpart")
library("rattle")
library("rpart.plot")
library("tinytex")
library("kableExtra")
library("ROSE")
library("tibble")
library("bitops")
library("tidyquant")
library("knitr")
library("plotly")
library("Sim.DiffProc")
library("readxl")
library("usethis")
library("curl")
library("dplyr")
library("tidyr")
library("scales")
library("RColorBrewer")
library("forcats")
library("ggrepel")
```

# Data Analysis 

## Data Reported in Sistema de Información Infonavit 2013/01-2021/04

Information regarding all mortgages originated by Infonavit from January 2013 to April 2021.

https://portalmx.infonavit.org.mx/wps/portal/infonavit.web/el-instituto/el-infonavit/SII/!ut/p/z1/pZBBDoIwFETP4gn-FJHWJRosFQKiqUA3pitCoujCeH7RJcSKcXY_eTN_MmSoItPZR9vYe3vt7Lm_axOcAgnEa59lQh05iijwc873yAWncgCkyQIFdonEFuzAQOYfv_am-T0ByBVYJkUsEG4iFS3TuSc1m-bHB4U_9x8Bxh1fkhm8GC_oBF4TvQHXBt9a3C66V4VWNbMnVfmrRQ!!/dz/d5/L2dBISEvZ0FBIS9nQSEh/

```{r LoadingData1}
# Número de Créditos Formalizados
NCTotal<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 1))
MCTipoProducto<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 2))
NCLinea<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 3))
NCClasificacionVivienda<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 4))
NCIngreso<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 5))
NCEdad<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 6))
NCEstado<-as.data.frame(read_excel("DATA/NumeroDeCreditosFormalizados.xlsx", sheet = 7))
## Totales
NC_TP<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=1))
NC_L<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=2))
NC_CV<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=3))
NC_I<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=4))
NC_Edad<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=5))
NC_Estado<-as.data.frame(read_excel("DATA/Totales/NC.xlsx",sheet=6))


# Importe de Cheque
ITotal<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 1))
ITipoProducto<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 2))
ILinea<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 3))
IClasificacionVivienda<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 4))
IIngreso<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 5))
IEdad<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 6))
IEstado<-as.data.frame(read_excel("DATA/ImporteDeCheque.xlsx", sheet = 7))
## Totales
I_TP<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=1))
I_L<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=2))
I_CV<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=3))
I_I<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=4))
I_Edad<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=5))
I_Estado<-as.data.frame(read_excel("DATA/Totales/I.xlsx",sheet=6))


# Monto de Crédito Infonavit
MCTotal<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 1))
MCTipoProducto<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 2))
MCLinea<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 3))
MCClasificacionVivienda<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 4))
MCIngreso<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 5))
MCEdad<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 6))
MCEstado<-as.data.frame(read_excel("DATA/MontoDeCreditoInfonavit.xlsx", sheet = 7))
## Totales
MC_TP<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=1))
MC_L<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=2))
MC_CV<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=3))
MC_I<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=4))
MC_Edad<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=5))
MC_Estado<-as.data.frame(read_excel("DATA/Totales/MC.xlsx",sheet=6))


# Número de Subsidios
NSTotal<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 1))
NSTipoProducto<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 2))
NSLinea<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 3))
NSClasificacionVivienda<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 4))
NSIngreso<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 5))
NSEdad<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 6))
NSEstado<-as.data.frame(read_excel("DATA/NumeroDeSubsidios.xlsx", sheet = 7))
## Totales
NS_TP<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=1))
NS_L<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=2))
NS_CV<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=3))
NS_I<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=4))
NS_Edad<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=5))
NS_Estado<-as.data.frame(read_excel("DATA/Totales/NS.xlsx",sheet=6))


# Monto de Subsidios
MSTotal<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 1))
MSTipoProducto<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 2))
MSLinea<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 3))
MSClasificacionVivienda<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 4))
MSIngreso<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 5))
MSEdad<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 6))
MSEstado<-as.data.frame(read_excel("DATA/MontoDeSubsidios.xlsx", sheet = 7))
## Totales
MS_TP<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=1))
MS_L<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=2))
MS_CV<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=3))
MS_I<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=4))
MS_Edad<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=5))
MS_Estado<-as.data.frame(read_excel("DATA/Totales/MS.xlsx",sheet=6))

# Recaudación y Fiscalización de las Aportaciones Patronales
RFAP<-as.data.frame(read_excel("DATA/RecaudacionYFiscalizacionDeAportacionesPatronales.xlsx", sheet = 1))

# Administración de la Subcuenta de Vivienda
ASV<-as.data.frame(read_excel("DATA/AdminSubcuentaDeVivienda.xlsx", sheet = 1))
```

### Number of Credits Granted 
```{r TotalsNC_CODE}
# Por Estado
barplot_NC_Estado<-ggplot(data=NC_Estado)+
  geom_bar(aes(x=reorder(Estado,-NC),y=NC,fill=Estado),stat = "identity")+
  geom_text(aes(x=Estado,y=NC,label=NC),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "Number of loans granted",
        title ="Loan distribution per State",
        subtitle = "2013/01 - 2021/04"
        )+
  ylim(0,625000)+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Estado como porcentaje
percent_Estado<-paste(round(100*(NC_Estado$NC/(sum(NC_Estado$NC))), 2), "%", sep="")
NC_Estado$percent<-percent_Estado

barplot_NC_Estado_percent<-ggplot(data=NC_Estado)+
  geom_bar(aes(x=reorder(Estado,-NC),y=NC,fill=Estado),stat = "identity")+
  geom_text(aes(x=Estado,y=NC,label=percent_Estado),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "% / Total Loans Granted",
        title ="Loan distribution per State",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )+ylim(0,625000)
  

# Por Tipo de Producto
percent_TP<-paste(round(100*(NC_TP$NC/(sum(NC_TP$NC))), 2), "%", sep="")
NC_TP$percent=percent_TP

piechart_NC_TP<-ggplot(data=NC_TP, aes(x="", y=NC, fill=TipoProducto)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_TP), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),arrow=TRUE) +
  guides(fill = guide_legend(title = "Product Type"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Loan Distribution by Product Type",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Clasificación de Vivienda
percent_CV<-paste(round(100*(NC_CV$NC/(sum(NC_CV$NC))), 2), "%", sep="")
NC_CV$percent=percent_CV

piechart_NC_CV<-ggplot(data=NC_CV, aes(x="", y=NC, fill=ClasificacionVivienda)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_CV), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),arrow=TRUE) +
  guides(fill = guide_legend(title = "Dwelling Classification"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Loan Distribution by Dwelling Classification",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Linea
percent_L<-paste(round(100*(NC_L$NC/(sum(NC_L$NC))), 2), "%", sep="")
NC_L$percent=percent_L

piechart_NC_L<-ggplot(data=NC_L, aes(x="", y=NC, fill=Linea)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_L), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),arrow=TRUE) +
  guides(fill = guide_legend(title = "Credit Line"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Loan Distribution by Credit Line",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Ingreso
UMA<-c("1","1-2","2-3","3-4","4-5","5-6","6-7","7-8","8-9","9-10","10-11","11-12","12-13","13-14","14-15","15-16","16-17","17-18","18-19","19-20","20-21","21-22","22-23","23-24","24-25","25+","Other")
NC_I$UMA<-UMA

barplot_NC_I<-ggplot(data=NC_I)+
  geom_bar(aes(x=reorder(UMA,-NC),y=NC,fill=UMA),stat = "identity")+
  geom_text(aes(x=UMA,y=NC,label=NC),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(NC_I)))+
  labs( x = "Income (UMA)", 
        y = "Number of loans granted",
        title ="Loans distribution by Income (UMA)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )+
  coord_cartesian(ylim=c(0,1300000))

# Por Edad
Edad2<-c("20","21-25","26-30","31-35","36-40","41-45","46-50","51-55","56-60","61-65","65+","Otros")
NC_Edad$Edad2<-Edad2

barplot_NC_Edad<-ggplot(data=NC_Edad)+
  geom_bar(aes(x=Edad2,y=NC,fill=Edad2),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(NC_I)))+
  labs( x = "Age group", 
        y = "Number of loans granted",
        title ="Loan distribution by Age",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=6,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )
```
```{r TotalsNC_GRAPHS, fig.align='center'}
barplot_NC_Estado
barplot_NC_Estado_percent
piechart_NC_TP
piechart_NC_CV
barplot_NC_I
piechart_NC_L
barplot_NC_Edad
```

### Credit Amount (MXN)
```{r TotalsMC_CODE}
# Por Estado
barplot_MC_Estado<-ggplot(data=MC_Estado)+
  geom_bar(aes(x=reorder(Estado,-MC),y=MC,fill=Estado),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "Credit amount (MXN)",
        title ="Total Amount of Granted Credit by State",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Estado como porcentaje
percent_Estado2<-paste(round(100*(MC_Estado$MC/(sum(MC_Estado$MC))), 2), "%", sep="")
MC_Estado$percent<-percent_Estado2

barplot_MC_Estado_percent<-ggplot(data=MC_Estado)+
  geom_bar(aes(x=reorder(Estado,-MC),y=MC,fill=Estado),stat = "identity")+
  geom_text(aes(x=Estado,y=MC,label=percent_Estado2),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "% / Total Amount of Credit",
        title ="Total Amount of Granted Credit by State (%)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )+ylim(0,143000000000)

# Por Tipo de Producto
percent_TP2<-paste(round(100*(MC_TP$MC/(sum(MC_TP$MC))), 2), "%", sep="")
MC_TP$percent=percent_TP2

piechart_MC_TP<-ggplot(data=MC_TP, aes(x="", y=MC, fill=TipoProducto)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_TP2), size=3, show.legend = F, position = position_stack(vjust = 0.5),max.overlaps = Inf) +
  guides(fill = guide_legend(title = "Product Type"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Total Amount of Granted Credit by Product Type",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Clasificación de Vivienda
percent_CV2<-paste(round(100*(MC_CV$MC/(sum(MC_CV$MC))), 2), "%", sep="")
MC_CV$percent=percent_CV2

piechart_MC_CV<-ggplot(data=MC_CV, aes(x="", y=MC, fill=ClasificacionVivienda)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_CV2), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),arrow=TRUE) +
  guides(fill = guide_legend(title = "Dwelling Classification"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Total Amount of Granted Credit by Dwelling Classification",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Linea
percent_L2<-paste(round(100*(MC_L$MC/(sum(MC_L$MC))), 2), "%", sep="")
MC_L$percent=percent_L2

piechart_MC_L<-ggplot(data=MC_L, aes(x="", y=MC, fill=Linea)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_L2), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),arrow=TRUE) +
  guides(fill = guide_legend(title = "Credit Line"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Total Amount of Granted Credit by Credit Line",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Ingreso
MC_I$UMA<-UMA

barplot_MC_I<-ggplot(data=MC_I)+
  geom_bar(aes(x=reorder(UMA,-MC),y=MC,fill=UMA),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(MC_I)))+
  labs( x = "Income (UMA)", 
        y = "Credit Amount (MXN)",
        title ="Total Amount of Granted Credit by Income (UMA)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Edad
MC_Edad$Edad2<-Edad2

barplot_MC_Edad<-ggplot(data=MC_Edad)+
  geom_bar(aes(x=Edad2,y=MC,fill=Edad2),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(MC_I)))+
  labs( x = "Age group", 
        y = "Credit Amount (MXN)",
        title ="Total Amount of Granted Credit by Age",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=6,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )
```
```{r TotalsMC_GRAPHS, fig.align='center'}
barplot_MC_Estado
barplot_MC_Estado_percent
piechart_MC_TP
piechart_MC_CV
piechart_MC_L
barplot_MC_I
barplot_MC_Edad
```

### Subsidies

#### Number
```{r TotalsNS_CODE}

# Por Estado
barplot_NS_Estado<-ggplot(data=NS_Estado)+
  geom_bar(aes(x=reorder(Estado,-NS),y=NS,fill=Estado),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "Number of Subsidies",
        title ="Number of Granted Subsidies by State",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Estado como porcentaje
percent_Estado3<-paste(round(100*(NS_Estado$NS/(sum(NS_Estado$NS))), 2), "%", sep="")
NS_Estado$percent<-percent_Estado3

barplot_NS_Estado_percent<-ggplot(data=NS_Estado)+
  geom_bar(aes(x=reorder(Estado,-NS),y=NS,fill=Estado),stat = "identity")+
  geom_text(aes(x=Estado,y=NS,label=percent_Estado3),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "% / Total Subsidies Granted",
        title ="Number of Granted Subsidies by State (%)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Tipo de Producto
# No Aplica: Todos son crédito tradicional

# Por Clasificación de Vivienda
percent_CV3<-paste(round(100*(NS_CV$NS/(sum(NS_CV$NS))), 2), "%", sep="")
NS_CV$percent=percent_CV3

piechart_NS_CV<-ggplot(data=NS_CV, aes(x="", y=NS, fill=ClasificacionVivienda)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_CV3), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),max.overlaps = Inf) +
  guides(fill = guide_legend(title = "Dwelling Classification"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Distribution of Subsidies by Dwelling Classification",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Linea
percent_L3<-paste(round(100*(NS_L$NS/(sum(NS_L$NS))), 2), "%", sep="")
NS_L$percent=percent_L3

piechart_NS_L<-ggplot(data=NS_L, aes(x="", y=NS, fill=Linea)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_L3), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),max.overlaps = Inf) +
  guides(fill = guide_legend(title = "Credit Line"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Distribution of Subsidies by Credit Line",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Ingreso
NS_I$UMA<-UMA

barplot_NS_I<-ggplot(data=NS_I)+
  geom_bar(aes(x=reorder(UMA,-NS),y=NS,fill=UMA),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(NS_I)))+
  labs( x = "Income (UMA)", 
        y = "Number of Subsidies",
        title ="Number of Granted Subsidies by Income (UMA)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Edad
NS_Edad$Edad2<-Edad2

barplot_NS_Edad<-ggplot(data=NS_Edad)+
  geom_bar(aes(x=Edad2,y=NS,fill=Edad2),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(NS_I)))+
  labs( x = "Age group", 
        y = "Number of Subsidies",
        title ="Number of Granted Subsidies by Age",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=6,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )
```
```{r TotalsNS_GRAPHS, fig.align='center'}
barplot_NS_Estado
barplot_NS_Estado_percent
piechart_NS_CV
piechart_NS_L
barplot_NS_I
barplot_NS_Edad
```

#### Amount ($MXN)
```{r TotalsMS_CODE}
# Por Estado
barplot_MS_Estado<-ggplot(data=MS_Estado)+
  geom_bar(aes(x=reorder(Estado,-MS),y=MS,fill=Estado),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "Amount (MXN)",
        title ="Amount of Granted Subsidies by State",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Estado como porcentaje
percent_Estado4<-paste(round(100*(MS_Estado$MS/(sum(MS_Estado$MS))), 2), "%", sep="")
MS_Estado$percent<-percent_Estado4

barplot_MS_Estado_percent<-ggplot(data=MS_Estado)+
  geom_bar(aes(x=reorder(Estado,-MS),y=MS,fill=Estado),stat = "identity")+
  geom_text(aes(x=Estado,y=MS,label=percent_Estado4),hjust=-0.2, size=2.5,angle=90)+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(32))+
  labs( x = "State", 
        y = "% / Total Amount",
        title ="Amount of Granted Subsidies by State (%)",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=0,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Tipo de Producto
# No Aplica: Todos son crédito tradicional

# Por Clasificación de Vivienda
percent_CV4<-paste(round(100*(MS_CV$MS/(sum(MS_CV$MS))), 2), "%", sep="")
MS_CV$percent=percent_CV4

piechart_MS_CV<-ggplot(data=MS_CV, aes(x="", y=MS, fill=ClasificacionVivienda)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_CV4), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),max.overlaps = Inf) +
  guides(fill = guide_legend(title = "Dwelling Classification"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Amount of Subsidies by Dwelling Classification",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Linea
percent_L4<-paste(round(100*(MS_L$MS/(sum(MS_L$MS))), 2), "%", sep="")
MS_L$percent=percent_L4

piechart_MS_L<-ggplot(data=MS_L, aes(x="", y=MS, fill=Linea)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  geom_label_repel(aes(label = percent_L4), size=3.5, show.legend = F, position = position_stack(vjust = 0.5),max.overlaps = Inf) +
  guides(fill = guide_legend(title = "Credit Line"))+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(8))+
  labs(
    y="",
    x="",
    title="Amount of Subsidies by Credit Line",
    subtitle="2013/01 - 2021/04"
  )+
  theme(
    plot.title = element_text(hjust=0.5),
    plot.subtitle = element_text(hjust=0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid  = element_blank()
  )

# Por Ingreso
MS_I$UMA<-UMA

barplot_MS_I<-ggplot(data=MS_I)+
  geom_bar(aes(x=reorder(UMA,-MS),y=MS,fill=UMA),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(MS_I)))+
  labs( x = "Income (UMA)", 
        y = "Amount (MXN)",
        title ="Amount of Granted Subsidies by Income",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=8,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )

# Por Edad
MS_Edad$Edad2<-Edad2

barplot_MS_Edad<-ggplot(data=MS_Edad)+
  geom_bar(aes(x=Edad2,y=MS,fill=Edad2),stat = "identity")+
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(nrow(MS_I)))+
  labs( x = "Age group", 
        y = "Amount (MXN)",
        title ="Amount of Granted Subsidies by Age",
        subtitle = "2013/01 - 2021/04"
        )+
  theme(
    axis.text.x=element_text(size=8,angle=45,hjust=1),
    axis.text.y=element_text(size=6,angle=45),
    plot.title = element_text(hjust=0.5),
    plot.subtitle=element_text(hjust=0.5),
    legend.position = "none"
    )
```
```{r TotalsMS_GRAPHS, fig.align='center'}
barplot_MS_Estado
barplot_MS_Estado_percent
piechart_MS_CV
piechart_MS_L
barplot_MS_I
barplot_MS_Edad
```

Solo para ver seasonality en el número de créditos otorgados por mes:
```{r TimeSeries, fig.align='center'}
timeseries_NCTotal<-ggplot(data=NCTotal)+
  geom_line(aes(x=Fecha,y=TotalNacional))
timeseries_NCTotal
```

## "Sistema de Información Infonavit": Complete Portfolio Analysis

https://portalmx.infonavit.org.mx/wps/portal/infonavit.web/transparencia/estaditicas/!ut/p/z1/jY_BCsIwEEQ_aTdNSdZjUmtalKQFQ-tepCcJaPUgfr8iXjwYO7eBNzMMMIzA8_RIp-mervN0fvkDq6NyiE1VCh_MtsSebIdWd1IZDcMbKAjRWRTeUUNoNnVbr3aycFEAL8njDxlcls8AnK8fgL8nnCXC3u29rUKQtNYfIHfx38jtEuOIqX0C2OrEmg!!/dz/d5/L2dBISEvZ0FBIS9nQSEh/

Leaving behind the database of "otorgamiento de crédito" we now consider the information reported in the section "Estadísticas", which gives portfolio operating indicators of Infonavit's **complete** portfolio. The database decomposes Infonavit's portfolio by: past due portfolio (vencida), extension portfolio (prórrroga) and current portfolio (vigente). 

Note that, before, we were analyzing credits originated from January 2013 to April 2021, but this new database includes mortgages originated **before** 2013, considering the **complete portfolio** as of 30th of April, 2021.

```{r LoadingData2}
# Complete Portfolio (CP) composition
CP_cuentas<-as.data.frame(read_excel("DATA/CarteraVencida.xlsx", sheet = 1))
CP_saldos<-as.data.frame(read_excel("DATA/CarteraVencida.xlsx", sheet = 2))
```
```{r CompletePortfolio_CODE}
# Panel con cuatro gráficas, una gráfica por año: Barras por estado con el total 
# de cartera en número de cuentas. Cada barra apilada por vigente + prórroga + vencida
# PENDIENTE

# Panel con cuatro gráficas, una gráfica por año: Barras por estado con el total 
# de cartera en saldo (mdp MXN). Cada barra apilada por vigente + prórroga + vencida
# PENDIENTE

# Gráfica con la sheet 2 del excel, pero sos*
# PENDIENTE
```
```{r CompletePortfolio_GRAPHS}

```

# Sample data

Now, we consider our main database. This is the data from where we intend to develop our credit risk model; it describes credits originated from January 2013 to April 2021 *individually*, characterizing each beneficiary by different variables like age, gender, type of dwelling, etc.

In theory, this data base should be exactly the same as the data analyzed at the beginning, reported in "Sistema de Información Infonavit" for 2013/01-2021/04. However, we do not expect this database to be distributed exactly the same as the **complete portfolio** information. We intend to manipulate this sample to best resemble the complete portfolio, so that the credit risk model can more accurately represent reality.

## Data Analysis
```{r LoadingData3}
sample<-readRDS(file="DATA/MUESTRA.Rds")
head(sample)
tail(sample)
str(sample)
summary(sample)
```

```{r}
# GRÁFICAS DE GABRIEL* Pegar su code*
```

## Adjust Sample to Match Population's Characteristics 
```{r}
# Berny
```

## Asign Variable Status
```{r}
# Luly
```

# Credit Risk Model

## Logistic Regression
```{r}
```

## Evaluation
```{r}
```

## Regional Analysis & Clusters
```{r}
```

# Building a Cross-Subsidy Scheme

## Asigning an Interest Rate
```{r}
```

# Comparative Statics & Tests
```{r}
```