---
title: "Preprocessing Data"
author:
- Lourdes Sofía Elizondo Guajardo
- Daniela Diaz Delgado
- Bernardo Ortega Chávez
- Gabriel González Bataller
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("gmodels")
library("ggplot2")
library("pROC")
library("rpart")
library("rattle")
library("rpart.plot")
library("tinytex")
library("kableExtra")
library("ROSE")
library("tibble")
library("bitops")
library("tidyquant")
library("knitr")
library("plotly")
library("Sim.DiffProc")
library("readxl")
library("usethis")
library("curl")
library("dplyr")
library("tidyr")
library("scales")
library("RColorBrewer")
library("forcats")
library("ggrepel")
library("gridExtra")

library('tseries')
library("quantmod")
library("urca")
library("fpp2")
library('feasts')
library('features')
library('fabletools')
```

# National Data Set

## Loading and visualizing the data

```{r}
BDT2 <- read_excel("BDF.xlsx")
DATA.ts <- ts(BDT2, start = c(2005, 2), frequency = 4)
CV <- DATA.ts[ ,1]
INPC <- DATA.ts[ ,2]
INPC_AB <- DATA.ts[ ,3]
INPC_SERV <- DATA.ts[ ,4]
INPC_T<- DATA.ts[ ,5]
INPC_E <- DATA.ts[ ,6]
IPV <- DATA.ts[ ,7]
IPC_SUB <- DATA.ts[ ,8]
IPC_NSUB <- DATA.ts[ ,9]
REMESAS <- DATA.ts[ ,10]
CPMI <- DATA.ts[ ,11]
INT <- DATA.ts[ ,12]
CONF <- DATA.ts[ ,13]
M1 <- DATA.ts[ ,14]
DEBT <- DATA.ts[ ,15]
EX <- DATA.ts[ ,16]
INFLACION <- DATA.ts[,17]
PIB <- DATA.ts[,18]
DESEMPLEO <- DATA.ts[,19]
DESEMPLEO_H <- DATA.ts[,20]
DESEMPLEO_M <- DATA.ts[,21]

# PLOTS
DataG1 <- ts(cbind(CV,INPC, INPC_AB, INPC_E,INPC_SERV,INPC_T,IPC_SUB, IPC_NSUB),start=c(2005,2),frequency=4)
DataG2 <- ts(cbind(CV, IPV, REMESAS, CPMI, INT, CONF, M1, DEBT, EX),start=c(2005,2),frequency=4)
DataG3 <- ts(cbind(CV, DESEMPLEO, DESEMPLEO_H, DESEMPLEO_M, INFLACION, PIB),start=c(2005,2),frequency=4)
plot(DataG1)
plot(DataG2)
plot(DataG3)
```

## Correlation

```{r}
round(cor(DATA.ts), 2)
```

## Stationarity

For all cases, the test-statistic is smaller than the critiral value. All variables are stationary.

```{r}
INPC.DF=ur.df(INPC, type = "trend", lags = 0)
summary(INPC.DF)

INPC_AB.DF=ur.df(INPC_AB, type = "trend", lags = 0)
summary(INPC_AB.DF)

INPC_SERV.DF=ur.df(INPC_SERV, type = "trend", lags = 0)
summary(INPC_SERV.DF)

INPC_T.DF=ur.df(INPC_T, type = "trend", lags = 0)
summary(INPC_T.DF)

INPC_E.DF=ur.df(INPC_E, type = "trend", lags = 0)
summary(INPC_E.DF)

IPV.DF=ur.df(IPV, type = "trend", lags = 0)
summary(IPV.DF)

IPC_SUB.DF=ur.df(IPC_SUB, type = "trend", lags = 0)
summary(IPC_SUB.DF)

IPC_NSUB.DF=ur.df(IPC_NSUB, type = "trend", lags = 0)
summary(IPC_NSUB.DF)

REMESAS.DF=ur.df(REMESAS, type = "trend", lags = 0)
summary(REMESAS.DF)

CPMI.DF=ur.df(CPMI, type = "trend", lags = 0)
summary(CPMI.DF)

INT.DF=ur.df(INT, lags = 0)
summary(INT.DF)

CONF.DF=ur.df(CONF, type = "trend", lags = 0)
summary(CONF.DF)

M1.DF=ur.df(M1, type = "trend", lags = 0)
summary(M1.DF)

DEBT.DF=ur.df(DEBT, type = "trend", lags = 0)
summary(DEBT.DF)

EX.DF=ur.df(EX, type = "trend", lags = 0)
summary(EX.DF)

INFLACION.DF=ur.df(INFLACION, type = "trend", lags = 0)
summary(INFLACION.DF)

DESEMPLEO.DF=ur.df(DESEMPLEO, type = "trend", lags = 0)
summary(DESEMPLEO.DF)

DESEMPLEO_H.DF=ur.df(DESEMPLEO_H, type = "trend", lags = 0)
summary(DESEMPLEO_H.DF)

DESEMPLEO_M.DF=ur.df(DESEMPLEO_M, type = "trend", lags = 0)
summary(DESEMPLEO_M.DF)
```

# State Data Set

## Loading and visualizing the data: 32 states

```{r}
AGS<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 1)), start=c(2005,2), end=c(2020,4),  frequency=4)
BC<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 2)), start=c(2005,2), end=c(2020,4),   frequency=4)
BCS<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 3)), start=c(2005,2), end=c(2020,4),   frequency=4)
CAMP<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 4)), start=c(2005,2), end=c(2020,4),   frequency=4)
CDMX<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 5)), start=c(2005,2), end=c(2020,4),   frequency=4)
CHIH<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 6)), start=c(2005,2), end=c(2020,4),   frequency=4)
CHIS<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 7)), start=c(2005,2), end=c(2020,4),   frequency=4)
COAH<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 8)), start=c(2005,2), end=c(2020,4),   frequency=4)
COL<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 9)), start=c(2005,2), end=c(2020,4),   frequency=4)
DGO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 10)), start=c(2005,2), end=c(2020,4),   frequency=4)
GRO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 11)), start=c(2005,2), end=c(2020,4),   frequency=4)
GTO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 12)), start=c(2005,2), end=c(2020,4),   frequency=4)
HGO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 13)), start=c(2005,2), end=c(2020,4),   frequency=4)
JAL<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 14)), start=c(2005,2), end=c(2020,4),   frequency=4)
MEX<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 15)), start=c(2005,2), end=c(2020,4),   frequency=4)
MICH<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 16)), start=c(2005,2), end=c(2020,4),   frequency=4)
MOR<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 17)), start=c(2005,2), end=c(2020,4),   frequency=4)
NAY<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 18)), start=c(2005,2), end=c(2020,4),   frequency=4)
NL<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 19)), start=c(2005,2),  end=c(2020,4),  frequency=4)
OAXACA<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 20)), start=c(2005,2), end=c(2020,4),   frequency=4)
PUE<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 21)), start=c(2005,2), end=c(2020,4),   frequency=4)
Q_ROO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 22)), start=c(2005,2), end=c(2020,4),   frequency=4)
QRO<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 23)), start=c(2005,2), end=c(2020,4),   frequency=4)
SIN<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 24)), start=c(2005,2), end=c(2020,4),   frequency=4)
SLP<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 25)), start=c(2005,2), end=c(2020,4),   frequency=4)
SON<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 26)), start=c(2005,2), end=c(2020,4),   frequency=4)
TAB<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 27)), start=c(2005,2), end=c(2020,4),   frequency=4)
TAMPS<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 28)), start=c(2005,2), end=c(2020,4),    frequency=4)
TLAX<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 29)), start=c(2005,2), end=c(2020,4),   frequency=4)
VER<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 30)), start=c(2005,2), end=c(2020,4),   frequency=4)
YUC<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 31)), start=c(2005,2), end=c(2020,4),   frequency=4)
ZAC<-ts(data=(read_excel("ESTADOS.xlsx", sheet = 32)), start=c(2005,2), end=c(2020,4),   frequency=4)

CV_AGS <- AGS[ ,5]
IPV_AGS <- AGS[ ,4]
GDP_AGS <- AGS[,6]
REM_AGS <- AGS[,10]
UNEMP_AGS <- AGS[,11]
DEBT_AGS <- AGS[,12]
plot_AGS<-ts(cbind(CV_AGS,IPV_AGS,GDP_AGS,REM_AGS,UNEMP_AGS,DEBT_AGS),start=c(2005,2),frequency=4)
plot(plot_AGS)

CV_BC <- BC[ ,5]
IPV_BC <- BC[ ,4]
GDP_BC <- BC[,6]
REM_BC <- BC[,10]
UNEMP_BC <- BC[,11]
DEBT_BC <- BC[,12]
plot_BC<-ts(cbind(CV_BC,IPV_BC,GDP_BC,REM_BC,UNEMP_BC,DEBT_BC),start=c(2005,2),frequency=4)
plot(plot_BC)

CV_BCS <- BCS[ ,5]
IPV_BCS <- BCS[ ,4]
GDP_BCS <- BCS[,6]
REM_BCS <- BCS[,10]
UNEMP_BCS <- BCS[,11]
DEBT_BCS <- BCS[,12]
plot_BCS<-ts(cbind(CV_BCS,IPV_BCS,GDP_BCS,REM_BCS,UNEMP_BCS,DEBT_BCS),start=c(2005,2),frequency=4)
plot(plot_BCS)

CV_CAMP <- CAMP[ ,5]
IPV_CAMP <- CAMP[ ,4]
GDP_CAMP <- CAMP[,6]
REM_CAMP <- CAMP[,10]
UNEMP_CAMP <- CAMP[,11]
DEBT_CAMP <- CAMP[,12]
plot_CAMP<-ts(cbind(CV_CAMP,IPV_CAMP,GDP_CAMP,REM_CAMP,UNEMP_CAMP,DEBT_CAMP),start=c(2005,2),frequency=4)
plot(plot_CAMP)

CV_CHIS <- CHIS[ ,5]
IPV_CHIS <- CHIS[ ,4]
GDP_CHIS <- CHIS[,6]
REM_CHIS <- CHIS[,10]
UNEMP_CHIS <- CHIS[,11]
DEBT_CHIS <- CHIS[,12]
plot_CHIS<-ts(cbind(CV_CHIS,IPV_CHIS,GDP_CHIS,REM_CHIS,UNEMP_CHIS,DEBT_CHIS),start=c(2005,2),frequency=4)
plot(plot_CHIS)

CV_CHIH <- CHIH[ ,5]
IPV_CHIH <- CHIH[ ,4]
GDP_CHIH <- CHIH[,6]
REM_CHIH <- CHIH[,10]
UNEMP_CHIH <- CHIH[,11]
DEBT_CHIH <- CHIH[,12]
plot_CHIH<-ts(cbind(CV_CHIH,IPV_CHIH,GDP_CHIH,REM_CHIH,UNEMP_CHIH,DEBT_CHIH),start=c(2005,2),frequency=4)
plot(plot_CHIH)

CV_CDMX <- CDMX[ ,5]
IPV_CDMX <- CDMX[ ,4]
GDP_CDMX <- CDMX[,6]
REM_CDMX <- CDMX[,10]
UNEMP_CDMX <- CDMX[,11]
DEBT_CDMX <- CDMX[,12]
plot_CDMX<-ts(cbind(CV_CDMX,IPV_CDMX,GDP_CDMX,REM_CDMX,UNEMP_CDMX,DEBT_CDMX),start=c(2005,2),frequency=4)
plot(plot_CDMX)

CV_COAH <- COAH[ ,5]
IPV_COAH <- COAH[ ,4]
GDP_COAH <- COAH[,6]
REM_COAH <- COAH[,10]
UNEMP_COAH <- COAH[,11]
DEBT_COAH <- COAH[,12]
plot_COAH<-ts(cbind(CV_COAH,IPV_COAH,GDP_COAH,REM_COAH,UNEMP_COAH,DEBT_COAH),start=c(2005,2),frequency=4)
plot(plot_COAH)

CV_COL <- COL[ ,5]
IPV_COL <- COL[ ,4]
GDP_COL <- COL[,6]
REM_COL <- COL[,10]
UNEMP_COL <- COL[,11]
DEBT_COL <- COL[,12]
plot_COL<-ts(cbind(CV_COL,IPV_COL,GDP_COL,REM_COL,UNEMP_COL,DEBT_COL),start=c(2005,2),frequency=4)
plot(plot_COL)

CV_DGO <- DGO[ ,5]
IPV_DGO <- DGO[ ,4]
GDP_DGO <- DGO[,6]
REM_DGO <- DGO[,10]
UNEMP_DGO <- DGO[,11]
DEBT_DGO <- DGO[,12]
plot_DGO<-ts(cbind(CV_DGO,IPV_DGO,GDP_DGO,REM_DGO,UNEMP_DGO,DEBT_DGO),start=c(2005,2),frequency=4)
plot(plot_DGO)

CV_GTO <- GTO[ ,5]
IPV_GTO <- GTO[ ,4]
GDP_GTO <- GTO[,6]
REM_GTO <- GTO[,10]
UNEMP_GTO <- GTO[,11]
DEBT_GTO <- GTO[,12]
plot_GTO<-ts(cbind(CV_GTO,IPV_GTO,GDP_GTO,REM_GTO,UNEMP_GTO,DEBT_GTO),start=c(2005,2),frequency=4)
plot(plot_GTO)

CV_GRO <- GRO[ ,5]
IPV_GRO <- GRO[ ,4]
GDP_GRO <- GRO[,6]
REM_GRO <- GRO[,10]
UNEMP_GRO <- GRO[,11]
DEBT_GRO <- GRO[,12]
plot_GRO<-ts(cbind(CV_GRO,IPV_GRO,GDP_GRO,REM_GRO,UNEMP_GRO,DEBT_GRO),start=c(2005,2),frequency=4)
plot(plot_GRO)

CV_HGO <- HGO[ ,5]
IPV_HGO <- HGO[ ,4]
GDP_HGO <- HGO[,6]
REM_HGO <- HGO[,10]
UNEMP_HGO <- HGO[,11]
DEBT_HGO <- HGO[,12]
plot_HGO<-ts(cbind(CV_HGO,IPV_HGO,GDP_HGO,REM_HGO,UNEMP_HGO,DEBT_HGO),start=c(2005,2),frequency=4)
plot(plot_HGO)

CV_JAL <- JAL[ ,5]
IPV_JAL <- JAL[ ,4]
GDP_JAL <- JAL[,6]
REM_JAL <- JAL[,10]
UNEMP_JAL <- JAL[,11]
DEBT_JAL <- JAL[,12]
plot_JAL<-ts(cbind(CV_JAL,IPV_JAL,GDP_JAL,REM_JAL,UNEMP_JAL,DEBT_JAL),start=c(2005,2),frequency=4)
plot(plot_JAL)

CV_MEX <- MEX[ ,5]
IPV_MEX <- MEX[ ,4]
GDP_MEX <- MEX[,6]
REM_MEX <- MEX[,10]
UNEMP_MEX <- MEX[,11]
DEBT_MEX <- MEX[,12]
plot_MEX<-ts(cbind(CV_MEX,IPV_MEX,GDP_MEX,REM_MEX,UNEMP_MEX,DEBT_MEX),start=c(2005,2),frequency=4)
plot(plot_MEX)

CV_MICH <- MICH[ ,5]
IPV_MICH <- MICH[ ,4]
GDP_MICH <- MICH[,6]
REM_MICH <- MICH[,10]
UNEMP_MICH <- MICH[,11]
DEBT_MICH <- MICH[,12]
plot_MICH<-ts(cbind(CV_MICH,IPV_MICH,GDP_MICH,REM_MICH,UNEMP_MICH,DEBT_MICH),start=c(2005,2),frequency=4)
plot(plot_MICH)

CV_MOR <- MOR[ ,5]
IPV_MOR <- MOR[ ,4]
GDP_MOR <- MOR[,6]
REM_MOR <- MOR[,10]
UNEMP_MOR <- MOR[,11]
DEBT_MOR <- MOR[,12]
plot_MOR<-ts(cbind(CV_MOR,IPV_MOR,GDP_MOR,REM_MOR,UNEMP_MOR,DEBT_MOR),start=c(2005,2),frequency=4)
plot(plot_MOR)

CV_NAY <- NAY[ ,5]
IPV_NAY <- NAY[ ,4]
GDP_NAY <- NAY[,6]
REM_NAY <- NAY[,10]
UNEMP_NAY <- NAY[,11]
DEBT_NAY <- NAY[,12]
plot_NAY<-ts(cbind(CV_NAY,IPV_NAY,GDP_NAY,REM_NAY,UNEMP_NAY,DEBT_NAY),start=c(2005,2),frequency=4)
plot(plot_NAY)

CV_NL <- NL[ ,5]
IPV_NL <- NL[ ,4]
GDP_NL <- NL[,6]
REM_NL <- NL[,10]
UNEMP_NL <- NL[,11]
DEBT_NL <- NL[,12]
plot_NL<-ts(cbind(CV_NL,IPV_NL,GDP_NL,REM_NL,UNEMP_NL,DEBT_NL),start=c(2005,2),frequency=4)
plot(plot_NL)

CV_OAXACA <- OAXACA[ ,5]
IPV_OAXACA <- OAXACA[ ,4]
GDP_OAXACA <- OAXACA[,6]
REM_OAXACA <- OAXACA[,10]
UNEMP_OAXACA <- OAXACA[,11]
DEBT_OAXACA <- OAXACA[,12]
plot_OAXACA<-ts(cbind(CV_OAXACA,IPV_OAXACA,GDP_OAXACA,REM_OAXACA,UNEMP_OAXACA,DEBT_OAXACA),start=c(2005,2),frequency=4)
plot(plot_OAXACA)

CV_PUE <- PUE[ ,5]
IPV_PUE <- PUE[ ,4]
GDP_PUE <- PUE[,6]
REM_PUE <- PUE[,10]
UNEMP_PUE <- PUE[,11]
DEBT_PUE <- PUE[,12]
plot_PUE<-ts(cbind(CV_PUE,IPV_PUE,GDP_PUE,REM_PUE,UNEMP_PUE,DEBT_PUE),start=c(2005,2),frequency=4)
plot(plot_PUE)

CV_QRO <- QRO[ ,5]
IPV_QRO <- QRO[ ,4]
GDP_QRO <- QRO[,6]
REM_QRO <- QRO[,10]
UNEMP_QRO <- QRO[,11]
DEBT_QRO <- QRO[,12]
plot_QRO<-ts(cbind(CV_QRO,IPV_QRO,GDP_QRO,REM_QRO,UNEMP_QRO,DEBT_QRO),start=c(2005,2),frequency=4)
plot(plot_QRO)

CV_Q_ROO <- Q_ROO[ ,5]
IPV_Q_ROO <- Q_ROO[ ,4]
GDP_Q_ROO <- Q_ROO[,6]
REM_Q_ROO <- Q_ROO[,10]
UNEMP_Q_ROO <- Q_ROO[,11]
DEBT_Q_ROO <- Q_ROO[,12]
plot_Q_ROO<-ts(cbind(CV_Q_ROO,IPV_Q_ROO,GDP_Q_ROO,REM_Q_ROO,UNEMP_Q_ROO,DEBT_Q_ROO),start=c(2005,2),frequency=4)
plot(plot_Q_ROO)

CV_SLP <- SLP[ ,5]
IPV_SLP <- SLP[ ,4]
GDP_SLP <- SLP[,6]
REM_SLP <- SLP[,10]
UNEMP_SLP <- SLP[,11]
DEBT_SLP <- SLP[,12]
plot_SLP<-ts(cbind(CV_SLP,IPV_SLP,GDP_SLP,REM_SLP,UNEMP_SLP,DEBT_SLP),start=c(2005,2),frequency=4)
plot(plot_SLP)

CV_SIN <- SIN[ ,5]
IPV_SIN <- SIN[ ,4]
GDP_SIN <- SIN[,6]
REM_SIN <- SIN[,10]
UNEMP_SIN <- SIN[,11]
DEBT_SIN <- SIN[,12]
plot_SIN<-ts(cbind(CV_SIN,IPV_SIN,GDP_SIN,REM_SIN,UNEMP_SIN,DEBT_SIN),start=c(2005,2),frequency=4)
plot(plot_SIN)

CV_SON <- SON[ ,5]
IPV_SON <- SON[ ,4]
GDP_SON <- SON[,6]
REM_SON <- SON[,10]
UNEMP_SON <- SON[,11]
DEBT_SON <- SON[,12]
plot_SON<-ts(cbind(CV_SON,IPV_SON,GDP_SON,REM_SON,UNEMP_SON,DEBT_SON),start=c(2005,2),frequency=4)
plot(plot_SON)

CV_TAB <- TAB[ ,5]
IPV_TAB <- TAB[ ,4]
GDP_TAB <- TAB[,6]
REM_TAB <- TAB[,10]
UNEMP_TAB <- TAB[,11]
DEBT_TAB <- TAB[,12]
plot_TAB<-ts(cbind(CV_TAB,IPV_TAB,GDP_TAB,REM_TAB,UNEMP_TAB,DEBT_TAB),start=c(2005,2),frequency=4)
plot(plot_TAB)

CV_TAMPS <- TAMPS[ ,5]
IPV_TAMPS <- TAMPS[ ,4]
GDP_TAMPS <- TAMPS[,6]
REM_TAMPS <- TAMPS[,10]
UNEMP_TAMPS <- TAMPS[,11]
DEBT_TAMPS <- TAMPS[,12]
plot_TAMPS<-ts(cbind(CV_TAMPS,IPV_TAMPS,GDP_TAMPS,REM_TAMPS,UNEMP_TAMPS,DEBT_TAMPS),start=c(2005,2),frequency=4)
plot(plot_TAMPS)

CV_TLAX <- TLAX[ ,5]
IPV_TLAX <- TLAX[ ,4]
GDP_TLAX <- TLAX[,6]
REM_TLAX <- TLAX[,10]
UNEMP_TLAX <- TLAX[,11]
DEBT_TLAX <- TLAX[,12]
plot_TLAX<-ts(cbind(CV_TLAX,IPV_TLAX,GDP_TLAX,REM_TLAX,UNEMP_TLAX,DEBT_TLAX),start=c(2005,2),frequency=4)
plot(plot_TLAX)

CV_VER <- VER[ ,5]
IPV_VER <- VER[ ,4]
GDP_VER <- VER[,6]
REM_VER <- VER[,10]
UNEMP_VER <- VER[,11]
DEBT_VER <- VER[,12]
plot_VER<-ts(cbind(CV_VER,IPV_VER,GDP_VER,REM_VER,UNEMP_VER,DEBT_VER),start=c(2005,2),frequency=4)
plot(plot_VER)

CV_YUC <- YUC[ ,5]
IPV_YUC <- YUC[ ,4]
GDP_YUC <- YUC[,6]
REM_YUC <- YUC[,10]
UNEMP_YUC <- YUC[,11]
DEBT_YUC <- YUC[,12]
plot_YUC<-ts(cbind(CV_YUC,IPV_YUC,GDP_YUC,REM_YUC,UNEMP_YUC,DEBT_YUC),start=c(2005,2),frequency=4)
plot(plot_YUC)

CV_ZAC <- ZAC[ ,5]
IPV_ZAC <- ZAC[ ,4]
GDP_ZAC <- ZAC[,6]
REM_ZAC <- ZAC[,10]
UNEMP_ZAC <- ZAC[,11]
DEBT_ZAC <- ZAC[,12]
plot_ZAC<-ts(cbind(CV_ZAC,IPV_ZAC,GDP_ZAC,REM_ZAC,UNEMP_ZAC,DEBT_ZAC),start=c(2005,2),frequency=4)
plot(plot_ZAC)
```

## Correlation
```{r}
round(cor(plot_AGS),2)
round(cor(plot_BC),2)
round(cor(plot_BCS),2)
round(cor(plot_CAMP),2)
round(cor(plot_CHIS),2)
round(cor(plot_CHIH),2)
round(cor(plot_CDMX),2)
round(cor(plot_COAH),2)
round(cor(plot_COL),2)
round(cor(plot_DGO),2)
round(cor(plot_GTO),2)
round(cor(plot_GRO),2)
round(cor(plot_HGO),2)
round(cor(plot_JAL),2)
round(cor(plot_MEX),2)
round(cor(plot_MICH),2)
round(cor(plot_MOR),2)
round(cor(plot_NAY),2)
round(cor(plot_NL),2)
round(cor(plot_OAXACA),2)
round(cor(plot_PUE),2)
round(cor(plot_QRO),2)
round(cor(plot_Q_ROO),2)
round(cor(plot_SLP),2)
round(cor(plot_SIN),2)
round(cor(plot_SON),2)
round(cor(plot_TAB),2)
round(cor(plot_TAMPS),2)
round(cor(plot_TLAX),2)
round(cor(plot_VER),2)
round(cor(plot_YUC),2)
round(cor(plot_ZAC),2)
```

## Stationarity

GDP, REM, UNEMP and DEBT are always stationary at a 99% confidence level.
IPV is always stationary, but only at a 95% confidence level.
CV is not stationary (at lags=0) in any case.
1 difference was enough to turn all CVs stationary.

```{r}
# Gabriel 1-8
# Dany 9-16
# Luly 17-24
# Berny 25-32

summary(ur.df(CV_MOR,lags=0))
CV_MOR_diff1<-diff(CV_MOR)
summary(ur.df(CV_MOR_diff1,lags=0))
plot(ts(cbind(CV_MOR,CV_MOR_diff1),start=c(2005,2),frequency=4))

summary(ur.df(IPV_MOR,lags=0))
summary(ur.df(GDP_MOR,lags=0))
summary(ur.df(REM_MOR,lags=0))
summary(ur.df(UNEMP_MOR,lags=0))
summary(ur.df(DEBT_MOR,lags=0))

summary(ur.df(CV_NAY,lags=0))
CV_NAY_diff1<-diff(CV_NAY)
summary(ur.df(CV_NAY_diff1,lags=0))
plot(ts(cbind(CV_NAY,CV_NAY_diff1),start=c(2005,2),frequency=4))

summary(ur.df(IPV_NAY,lags=0))
summary(ur.df(GDP_NAY,lags=0))
summary(ur.df(REM_NAY,lags=0))
summary(ur.df(UNEMP_NAY,lags=0))
summary(ur.df(DEBT_NAY,lags=0))

summary(ur.df(CV_NL,lags=0))
CV_NL_diff1<-diff(CV_NL)
summary(ur.df(CV_NL_diff1,lags=0))
plot(ts(cbind(CV_NL,CV_NL_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_NL,lags=0))
summary(ur.df(IPV_NL,lags=0))
summary(ur.df(GDP_NL,lags=0))
summary(ur.df(REM_NL,lags=0))
summary(ur.df(UNEMP_NL,lags=0))
summary(ur.df(DEBT_NL,lags=0))

summary(ur.df(CV_OAXACA,lags=0))
CV_OAXACA_diff1<-diff(CV_OAXACA)
summary(ur.df(CV_OAXACA_diff1,lags=0))
plot(ts(cbind(CV_OAXACA,CV_OAXACA_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_OAXACA,lags=0))
summary(ur.df(IPV_OAXACA,lags=0))
summary(ur.df(GDP_OAXACA,lags=0))
summary(ur.df(REM_OAXACA,lags=0))
summary(ur.df(UNEMP_OAXACA,lags=0))
summary(ur.df(DEBT_OAXACA,lags=0))

summary(ur.df(CV_PUE,lags=0))
CV_PUE_diff1<-diff(CV_PUE)
summary(ur.df(CV_PUE_diff1,lags=0))
plot(ts(cbind(CV_PUE,CV_PUE_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_PUE,lags=0))
summary(ur.df(IPV_PUE,lags=0))
summary(ur.df(GDP_PUE,lags=0))
summary(ur.df(REM_PUE,lags=0))
summary(ur.df(UNEMP_PUE,lags=0))
summary(ur.df(DEBT_PUE,lags=0))

summary(ur.df(CV_QRO,lags=0))
CV_QRO_diff1<-diff(CV_QRO)
summary(ur.df(CV_QRO_diff1,lags=0))
plot(ts(cbind(CV_QRO,CV_QRO_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_QRO,lags=0))
summary(ur.df(IPV_QRO,lags=0))
summary(ur.df(GDP_QRO,lags=0))
summary(ur.df(REM_QRO,lags=0))
summary(ur.df(UNEMP_QRO,lags=0))
summary(ur.df(DEBT_QRO,lags=0))

summary(ur.df(CV_Q_ROO,lags=0))
CV_Q_ROO_diff1<-diff(CV_Q_ROO)
summary(ur.df(CV_Q_ROO_diff1,lags=0))
plot(ts(cbind(CV_Q_ROO,CV_Q_ROO_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_Q_ROO,lags=0))
summary(ur.df(IPV_Q_ROO,lags=0))
summary(ur.df(GDP_Q_ROO,lags=0))
summary(ur.df(REM_Q_ROO,lags=0))
summary(ur.df(UNEMP_Q_ROO,lags=0))
summary(ur.df(DEBT_Q_ROO,lags=0))

summary(ur.df(CV_SIN,lags=0))
CV_SIN_diff1<-diff(CV_SIN)
summary(ur.df(CV_SIN_diff1,lags=0))
plot(ts(cbind(CV_SIN,CV_SIN_diff1),start=c(2005,2),frequency=4))

summary(ur.df(CV_SIN,lags=0))
summary(ur.df(IPV_SIN,lags=0))
summary(ur.df(GDP_SIN,lags=0))
summary(ur.df(REM_SIN,lags=0))
summary(ur.df(UNEMP_SIN,lags=0))
summary(ur.df(DEBT_SIN,lags=0))
```
